Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-07-06 cogsci/cogsci.Rmd
journal version

In the semantic case, the networks are based on free association norms. These associations can be derived from the patterns of word-word co-occurrence [e.g., @griffiths07], i.e., two words are associated if they co-occur in many different contexts. In a network structure, highly connected words would be the words that co-occur with many other words in various contexts. Why would such words be easier to learn? One possibility, suggested by @hills2010, is that the referents of these words are more easily disambiguated from other potential referents because their presence in multiple contexts provides more cross-situational, disambiguating statistics about their true referents [@smith2008].

>>>>

In the semantic case, the networks are based on free association norms. These associations can be (partly) derived from the patterns of word-word co-occurrence [e.g., @griffiths07], i.e., two words are associated if they co-occur in many different contexts. In a network structure, highly connected words would be the words that co-occur with many other words in various contexts. Why would such words be easier to learn? One possibility, suggested by @hills2010, is that the referents of these words are more easily disambiguated from other potential referents because their presence in multiple contexts provides more cross-situational, disambiguating statistics about their true referents [@smith2008].

### 2018-07-06 cogsci/cogsci.tex
journal version

In the semantic case, the networks are based on free association norms.
These associations can be derived from the patterns of word-word
co-occurrence (e.g., Griffiths, Steyvers, \& Tenenbaum, 2007), i.e., two
words are associated if they co-occur in many different contexts. In a
network structure, highly connected words would be the words that
co-occur with many other words in various contexts. Why would such words
be easier to learn? One possibility, suggested by Hills et al. (2010),
is that the referents of these words are more easily disambiguated from
other potential referents because their presence in multiple contexts
provides more cross-situational, disambiguating statistics about their
true referents (Smith \& Yu, 2008).

>>>>

In the semantic case, the networks are based on free association norms.
These associations can be (partly) derived from the patterns of
word-word co-occurrence (e.g., Griffiths, Steyvers, \& Tenenbaum, 2007),
i.e., two words are associated if they co-occur in many different
contexts. In a network structure, highly connected words would be the
words that co-occur with many other words in various contexts. Why would
such words be easier to learn? One possibility, suggested by Hills et
al. (2010), is that the referents of these words are more easily
disambiguated from other potential referents because their presence in
multiple contexts provides more cross-situational, disambiguating
statistics about their true referents (Smith \& Yu, 2008).
